Lossy compression of DNA sequencing quality data

### 2015-04-25 manuscript/q-compression.tex
Text edit.

No assembly of the \textit{Rhodobacter sphaeroides} 2.4.1 data set
outperforms all others in all metrics (Table
\ref{fig:assembly_ranks}).
%The assembly of the \textit{Rhodobacter sphaeroides} 2.4.1 data set
%using the uncompressed reads outperforms all compression methods in
%terms of \textsc{lap}, NG50, relocations, translations, and
%inversions.
Among the compression methods, the profile encoding performed best,
polynomial regression modeling with degree $>$ 7 performed worst, and
other methods were intermediate (Fig.~\ref{fig:assembly_ranks}).

>>>>

No assembly of the \textit{Rhodobacter sphaeroides} 2.4.1 data set
outperforms all others in all metrics (Table
\ref{fig:assembly_ranks}).
%The assembly of the \textit{Rhodobacter sphaeroides} 2.4.1 data set
%using the uncompressed reads outperforms all compression methods in
%terms of \textsc{lap}, NG50, relocations, translations, and
%inversions.
Among the compression methods, the profile encoding performed best,
polynomial regression modeling with degree $<=$ 7 performed worst, and
other methods were intermediate (Fig.~\ref{fig:assembly_ranks}).
